Representation Project

### 2024-12-09 docs/misc/outlier.qmd
minor link fix

>>>>

prob_exact <- posterior_preds[, , "Exact match"]
prob_minor <- posterior_preds[, , "0.01-2% error"]
prob_moderate <- posterior_preds[, , "2.01-15% error"]
prob_major <- posterior_preds[, , "Over 15% error"]

# Compute mean probabilities across all posterior samples
s2_agg_filtered <- s2_agg_filtered %>%
  mutate(
    prob_exact = colMeans(prob_exact),
    prob_minor = colMeans(prob_minor),
    prob_moderate = colMeans(prob_moderate),
    prob_major = colMeans(prob_major)
  )

emm_refClass_manual <- s2_agg_filtered %>%
  group_by(refClass) %>%
  summarise(
    mean_prob_exact = mean(prob_exact),
    mean_prob_minor = mean(prob_minor),
    mean_prob_moderate = mean(prob_moderate),
    mean_prob_major = mean(prob_major)
  )

print(emm_refClass_manual)

ggplot(emm_refClass_manual, aes(x = refClass)) +
  geom_bar(aes(y = mean_prob_exact), stat = "identity", fill = "steelblue") +
  geom_errorbar(aes(ymin = mean_prob_exact - 0.05, ymax = mean_prob_exact + 0.05), width = 0.2) +
  labs(title = "Estimated Marginal Means for Reference Class",
       x = "Reference Class",
       y = "Probability of Exact Match") +
  theme_minimal()
```

### 2024-12-09 paper.qmd
update results section. And some formating improvements.
minor link fix

@@

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/Manuscript/output/manuscript.docx">
  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;docx <small>(download)</small>
  </a>

>>>>

  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/manuscript-code.html" target="_blank">
   <i class="fa-solid fa-arrow-up-right-from-square"></i>&ensp;HTML <small>(with code)</small>
  </a>

@@

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/Manuscript/output/Manuscript.docx">
  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;docx <small>(download)</small>
  </a>
